\documentclass[a4paper,12pt]{letter}

% Some of the article customisations are relevant for this class

\name{} % To be used for the return address on the envelope
\signature{Rebecca Bucci} % Goes after the closing (ie at the end of the letter, with space for a signature)
\address{Address \\ of \\ Sender}
% Alternatively, these may be set on an individual basis within each letter environment.

%\makelabels % this command prints envelope labels on the final page of the document

\begin{document}
\begin{letter}{Name and \\ Address \\ of \\ Receiver}

\opening{} % eg Hello.

Dear , 

Please consider the attached manuscript entitled “”. This manuscript is not under review, in press, or published elsewhere in any form and there are no conflict of interests to report.
In this study, I rely on data collected from TESS… I examine… 

I find that 

The current study responds to a recent call for work which integrates ideas from behavioral economics into criminology to better understand offender decision-making (Pogarsky, Roche \& Pickett, 2018).

I believe this manuscript fits well with the aims of Criminology. 

Criminology has published some of the recent and influential work in this area ---- 
Pickett, Roche \& Pogarsky (2018)
Pogarsky, Roche \& Pickett (2017)

and more recently, work that has shown the importance of emotions in offender decision-making (Barnum \& Solomon, 2019). 


I appreciate your consideration of this manuscript. The manuscript is BLANK pages in length and BLANK words. It is formatted to match the Criminology submission guidelines. 


\closing{Kind regards,} % eg Regards,



\end{letter}
\end{document}
